### 2024-10-29 main_widom_morse.tex
change text to mentin three lines

In our previous work~\cite{KD20}, the equation of state for a many-particle system interacting via a modified Morse potential was developed in the framework of a cell model. Recently~\cite{DKRP24,DKRP24arxiv}, the thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, have been calculated for the same model system. The isothermal compressibility and thermal expansion coefficient both develop a maximum in some region beyond critical point. On the one hand, such response function maxima, as mentioned above, are considered as good candidates for crossover lines between gas-like and liquid-like behaviors in the supercritical region. On the other hand, they are also considered as natural continuation of the coexistence line. Since our model allows for analytical expressions for many thermodynamic quantities~\cite{KD20,DKRP24}, it is straightforward to calculate and build such continuations. As a logical sequence of our previous works for the cell model with the modified Morse potential, in this paper we present results for two lines that can be cosidered as continuations of the coexistence line beyond the critical point in the pressure-temperature plane. The first one is the locus of the isothermal compressibility maxima. This line, as will be shown, ends (disappears, ceases to exist) at some temperature above the critical one. The second one is a line that is derived from the same condition that the first-order phase transition line below the critical point - the condition on the effective chemical potential $M=0$. This line can be extended into the supercritical region without any limits in temperature or pressure.

In Section~\ref{sec:eos}, we recall the form of the modified Morse potential, present the explicit expression for the equation of state, and illustrate pressure isotherms at temperatures below and above the critical one. In Section~\ref{sec:widom}, we display the Widom line as the maxima locus of the isothermal compressibility and introduce the supercritical crossover line obtained directly from the equation of state of the cell fluid model applying the proper condition on the effective chemical potential.

>>>>

In our previous work~\cite{KD20}, the equation of state for a many-particle system interacting via a modified Morse potential was developed in the framework of a cell model. Recently~\cite{DKRP24,DKRP24arxiv}, the thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, have been calculated for the same model system. The isothermal compressibility and thermal expansion coefficient both develop a maximum in some region beyond critical point. On the one hand, such response function maxima, as mentioned above, are considered as good candidates for crossover lines between gas-like and liquid-like behaviors in the supercritical region. On the other hand, they are also considered as natural continuation of the coexistence line. Since our model allows for analytical expressions for many thermodynamic quantities~\cite{KD20,DKRP24}, it is straightforward to calculate and build such continuations. As a logical sequence of our previous works for the cell model with the modified Morse potential, in this paper we present results for three lines that can be cosidered as continuations of the coexistence line beyond the critical point in the pressure-temperature plane. The first one is the locus of the isothermal compressibility maxima. This line, as will be shown, terminates at some temperature above the critical one. The second line is the locus of the thermal expansion coefficient, which also terminates at some point. The third one is a line that is derived from the same condition that the first-order phase transition line below the critical point - the condition on the effective chemical potential $M=0$. This line can be extended into the supercritical region without any limits in temperature or pressure.

In Section~\ref{sec:eos}, we recall the form of the modified Morse potential, present the explicit expression for the equation of state, and illustrate pressure isotherms at temperatures below and above the critical one. In Section~\ref{sec:widom}, we develop two alternatives of the Widom line, as the maxima locus of the isothermal compressibility and as the locus of maxima of the thermal expansion coefficient. Then we introduce the supercritical crossover line obtained directly from the equation of state of the cell fluid model applying a condition on the effective chemical potential that is the same as is used below CP to obtain the coexistence line.
